Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-13 paper/ijcai/paper.tex
organizing and cleaning

\Mar{consider moving footnotes 1 and 2 to references.}
Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking 
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed. 
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
available.

@@

\section{The \sfl{}+\cs{} combination}
\label{sec:combination}

@@

@@

\begin{algorithm}[h]
	\caption{Function of interest (iFunc)}
	\label{alg:finc}
	\begin{flushleft}
		\textbf{Input:} $c$ - class to be minimized\\
		\hspace{2.75em} $t$ - testcase name\\
		\hspace{2.75em} $expStk$ -  expected stacktrace\\
		\textbf{Output:} $interest$ - $True$ if it is interesting, $False$ if not \\
	\end{flushleft}
	\begin{algorithmic}[1]
		\Function{iFunc}{$c$, $t$, $expStk$}
		\State $testStk \leftarrow$ runTest($t$)
		\State $testOracle \leftarrow$ getOracleToCompare($testStk$)
		\State $expOracle \leftarrow$ getOracleToCompare($expStk$)
		\State \Return $testOracle$ == $expOracle$
		\EndFunction

	\end{algorithmic}

\end{algorithm}

@@

Recall from Section~\ref{sec:combination} that the \comb{} combination
takes on input a value denoting the $k$ most suspicious distinct
files. To evaluate the effectiveness of \comb{}, we compared its
performance with \sfl{} for each defect on each subject program from
the dataset, for $k\in\{5,10\}$. These files are obtained directly
from the ranking. We refer to these variations as \combpar{k}. We
compared \combpar{5} and \combpar{10} against \sfl{} using the
following metrics.\Mar{Sofia, I don't see a reason for an equation to
  only show the difference of cost. Please describe precisely the
  metrics. In this case, I can't find what C stands for. Also,
 you need to describe precisely what top@n (or someother name) means
 in this context. Check if it makes sense for SFL.$\rightarrow$}

>>>>

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking 
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed. 
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
available.

@@

\section{Approach}
\label{sec:approach}

@@

\subsection{The \sfl{}+\cs{} combination}
\label{sec:comb}

@@

% \begin{algorithm}[h]
% 	\caption{Function of interest (iFunc)}
% 	\label{alg:finc}
% 	\begin{flushleft}
% 		\textbf{Input:} $c$ - class to be minimized\\
% 		\hspace{2.75em} $t$ - testcase name\\
% 		\hspace{2.75em} $expStk$ -  expected stacktrace\\
% 		\textbf{Output:} $interest$ - $True$ if it is interesting, $False$ if not \\
% 	\end{flushleft}
% 	\begin{algorithmic}[1]
% 		\Function{iFunc}{$c$, $t$, $expStk$}
% 		\State $testStk \leftarrow$ runTest($t$)
% 		\State $testOracle \leftarrow$ getOracleToCompare($testStk$)
% 		\State $expOracle \leftarrow$ getOracleToCompare($expStk$)
% 		\State \Return $testOracle$ == $expOracle$
% 		\EndFunction
%
% 	\end{algorithmic}
%
% \end{algorithm}

@@

Recall from Section~\ref{sec:approach} that the \comb{} combination
takes on input a value denoting the $k$ most suspicious distinct
files. To evaluate the effectiveness of \comb{}, we compared its
performance with \sfl{} for each defect on each subject program from
the dataset, for $k\in\{5,10\}$. These files are obtained directly
from the ranking. We refer to these variations as \combpar{k}. We
compared \combpar{5} and \combpar{10} against \sfl{} using the
following metrics.\Mar{Sofia, I don't see a reason for an equation to
  only show the difference of cost. Please describe precisely the
  metrics. In this case, I can't find what C stands for. Also,
 you need to describe precisely what top@n (or someother name) means
 in this context. Check if it makes sense for SFL.$\rightarrow$}
